\documentclass[12pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\usepackage{ifpdf}
\usepackage{indentfirst}
\usepackage{mla}

\MakeOuterQuote{"}

\begin{document}
    \begin{mla}{Tarik}{Onalan}{Calvert}{English}{20 April 2015}{Diseased, Abusive Love}
        \section{Thematic Statement}
            \noindent
            When physical desire becomes the only motivator in a relationship, the
            relationship becomes one-sided, with one individual forcing the other
            to fulfill their physical needs. Given that the forcing can be by any
            means seen fit, this lends itself to physical and emotional violence.
        \section{Quotes}
            \begin{itemize}
                \item "I would have kidnapped her and locked her up, and only I would have had
                    the key." (36)
                \item "[T]he young man she had never seen before kissed Rosa on the lips,
                    the neck, the breasts, and between the legs." (39)
                \item "He was whistling. She continued to weep. Before dropping her off at
                    her hut, the patron kissed her on the lips." (57)
                \item "Not a girl passed from puberty to adulthood that he did not subject
                    to the woods, the riverbank, or the wrought-iron bed." (63)
                \item "Trueba continued polishing his reputation as a rake, sowing the
                    entire region with his bastard offspring, reaping hatred" (63)
                \item "Barrabas became unstuck from his beloved, leaving her to die in the
                    courtyard" (78)
                \item "Esteban swore that sooner or later she would come to love him as he
                    needed to be loved, even if it meant he had to resort to extreme measures." (96)
                \item "[I]t was impossible to spice them up with the salt of evil or the
                    pepper of submission." (129)
                \item "Clara came to fear him far more than she had when he was [healthy]" (164)
                \item "It was the first time she had seen her father's temper turned against
                    her mother." (170)
                \item "One day, Clara had a bolt installed on her bedroom door and after that
                    she never let me in her bed again, except when I forced myself on her" (179)
                \item "I tried rape again, just to see if it would get a rise out of her." (181)
                \item "When he saw her, Esteban vented his rage on Clara." (200)
                \item "He lost control and struck her in the face, knocking her against
                    the wall." (200)
                \item "A year after I took my vows, she became a widow and began to come
                    to church and stare at me with languid eyes." (227)
                \item "The walls of Jean de Satigny's studio were covered with distressing
                    erotic scenes that revealed her husband's hidden character." (260)
                \item "Senator Trueba's relationship with his family only worsened with
                    time." (275)
                \item "He wanted to hurt her, destroy her, but he also wanted to continue
                    smelling her" (286)
                \item "Jaime and Nicolas lost what little interest they had in the family
                    and showed no compassion for their father" (297)
                \item "[I]n a flash the unchanged bride dissolved like a spell, disintegrating
                    into a fine gray powder." (305)
                \item "As soon as he was free again, he returned to Blanca, thinner, guiltier,
                    and with deeper rings under his eyes" (311)
                \item "[W]ilting flowers in their hands and not a single tear for the solitary
                    body they were laying to rest." (313)
                \item "Garcia's tongue tried to pry open her lips while his hand pressed
                    against her jaw until he forced it open." (327)
                \item "[H]e never let a day go by without seeing Alba, alternating unbridled
                    violence with the pretense that he was a good friend." (411)
                \item (413, \textsection2)
            \end{itemize}
            \centerline{Best Examples}
            \begin{enumerate}
                \item "[I]n a flash the unchanged bride dissolved like a spell, disintegrating
                    into a fine gray powder." (305)
                \item "He wanted to hurt her, destroy her, but he also wanted to continue
                    smelling her" (286)
                \item "[H]e never let a day go by without seeing Alba, alternating unbridled
                    violence with the pretense that he was a good friend." (411)
                \item (413, \textsection2)
                \item "He was whistling. She continued to weep. Before dropping her off at
                    her hut, the patron kissed her on the lips." (57)
                \item "[T]he young man she had never seen before kissed Rosa on the lips,
                    the neck, the breasts, and between the legs." (39)
                \item "One day, Clara had a bolt installed on her bedroom door and after that
                    she never let me in her bed again, except when I forced myself on her" (179)
                \item "Trueba continued polishing his reputation as a rake, sowing the
                    entire region with his bastard offspring, reaping hatred" (63)
                \item "Barrabas became unstuck from his beloved, leaving her to die in the
                    courtyard" (78)
                \item "A year after I took my vows, she became a widow and began to come
                    to church and stare at me with languid eyes." (227)
            \end{enumerate}
        \newpage
        \section{Paragraph}
            In the novel \textit{The House of the Spirits}, written by Isabel Allende
            and translated by Magda Bogin, Allende's contrast of characters' emotions
            and actions suggests that as a relationship begins to revolve around
            physical desire, the relationship becomes increasingly violent, both
            emotionally and physically. This is especially apparent with Esteban
            Garcia's relationship with Alba, where he would "[alternate] unbridled
            violence with the pretense that he was a good friend" (411). Evidently,
            the contrast arises from the alternation of "unbridled violence" and
            the "pretense that [Esteban Garcia] was a good friend". However, this
            is one half; noting that during this time "[Garcia] never let a day
            go by without seeing Alba" (411)---raping her daily---this contrast
            becomes more pronounced. Given that Alba and Garcia's relationship is
            purely physical---that is, not romantic---Allende's juxtaposition of
            Garcia's violent and friendly demeanors emphasizes the violence of his
            and Alba's relationship. Similar to Garcia and Alba, Esteban Trueba and
            Pancha Garcia's relationship was purely physical as well; before raping
            Pancha, Esteban decides "that he would have to find a woman" (56) to
            fulfill his physical desire. Allende's imagery of the rape describes
            "[Esteban] [attacking] [Pancha] savagely...with unnecessary brutality"
            (57). Note that only two of the three requirements defined above are met:
            physical relationship and violence. The key, contrast, is presented
            immediately after the image of Pancha's rape, where "[Esteban] [is]
            whistling" while "[Pancha] [continues] to weep" (57). This juxtaposition
            by Allende reinforces the idea that a purely physical relationship is
            inherently a violent one. However, Allende does not always directly present
            this idea. Rosa and Esteban's relationship at first seems to be nonviolent,
            though it is important to note that violence is not necessarily limited
            to physical forms; emotional violence---teasing, isolation, and others---
            is just as potent. Considering this, it would be fair to say that Rosa
            and Esteban's relationship was violent, as Esteban "lost two years
            dreaming of Rosa, working for Rosa, writing to Rosa, [and] wanting Rosa"
            (35), only for her to die, and for all his work to effectively be for
            naught. The fact that Rosa, in his eyes, "slipped through [his] hands"
            (34), punctuates the emotional violence of his and Rosa's relationship.
            Esteban's physical desire for Rosa is obvious; he notes that "[Rosa]
            was so beautiful...all [he] noticed was her face" (22). All of this
            is summed by Allende when Esteban unearths Rosa's coffin to take to
            the mausoleum, and as a result of his kiss Rosa's corpse "[disintegrates]
            into a fine gray powder" (305). Suddenly, Rosa is no longer a beautiful
            mermaid, but a decaying skeleton; more importantly, the Rosa the Beautiful
            that Esteban wants is now forever out of his reach, serving as the
            culmination of all of the teasing desire that Esteban experiences.
            In essence, Allende's use of contrast between characters' emotions
            and actions reveals the connection between physical desires and
            violence, a "skin-deep" marker for skin-deep emotions.
    \end{mla}
\end{document}
