%!TEX program = xelatex

\documentclass[a4paper,12pt]{article}

\usepackage{polyglossia}
\setdefaultlanguage{english}

\usepackage[backend=biber,style=mla,noremoteinfo=false]{biblatex}
\usepackage[autostyle]{csquotes}
\usepackage{hyperref}
\usepackage{setspace}

\renewcommand{\thesection}{\Roman{section}}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\doublespacing

\addbibresource{./Historical_Investigation.bib}

\begin{document}
    \input{./Historical_Investigation.title.tex}
    
    %--------------------------------------------------------------------------------------------------%

    \section{Plan of Investigation}

        The task of this investigation is to analyze to what extent the creation of the Manhattan
        project was a product of Germany's desire to expand between 1932 and 1942.

        The primary method of this investigation is to analyze accounts of the objectives of the
        Manhattan Project in the years before its inception to understand possible reasons behind
        its founding. This investigation will also analyze accounts of the interaction of the German
        and American propaganda machines to understand the influence Germany had on the global
        populace. Additionally, accounts of German expansion by Americans will be analyzed to
        understand to what extent the German expansion was viewed as a direct threat to America.

        This investigation will focus on two organizations: the Nazis of Germany, and the office of
        Franklin Delano Roosevelt. The scope of this investigation will be limited to sources
        pertaining to these organizations.

    %--------------------------------------------------------------------------------------------------%

    % Conversely, although Roosevelt
    % did respond to Szilard's 1939 petition by appointing a commission
    % to explore the exigencies of building an atomic weapon, U.S.
    % policymakers did not take energetic action to conceptualize, fund,
    % organize, and administer the enterprise until 1940-41, when attention
    % was much captivated by the war in the Pacific.
    %
    % Norris 12

    \section{Summary of Evidence}
        \begin{itemize}
            \item Fear of Germans and the Manhattan Project:
            \begin{itemize}
                \item American leadership perceived Germany as the only enemy with the capacity to take advantage of information taken from the Americans \cite[141]{grovesl}
                \item Security from Germany was one of the founding objectives of the Manhattan Project \cite[140]{grovesl}
                \item Leo Szilard---a physicist and refugee---brings information about German atomic weapons development and asks Roosevelt to pursue development, which led President Roosevelt to begin  atomic weapons research \cite[12]{norrism}
                \item America feared that Germany would produce an atomic weapon \cite[136]{stoffm}
            \end{itemize}
            \item Competition to produce weapons:
            \begin{itemize}
                \item German scientists went to Germany to contribute to atomic development against America \cite[6]{powerst}
                \item The US began atomic weapons development out of fear that the Germans would produce a similar weapon \cite[88]{steinbergg}
                \item The US began atomic weapons development to deter Germany's nuclear first-strike capability \cite[89]{steinbergg}
                \item Rockets could replace and outclass long-range guns, and constituted a loophole in the Versailles treaty \cite[2]{neufeldm}
                \item Rockets could be used to attack America with various payloads, thus making them appealing to Germans and fear-inducing to Americans \cite[157]{neufeldm}
            \end{itemize}
            \item Propaganda:
            \begin{itemize}
                \item American:
                \begin{itemize}
                    \item The American government controlled media outlets to spread propaganda against Nazi Germany \cite[2]{lauriec}
                    \item The Manhattan Project was indirectly used as deterrent against German expansion \cite[140]{grovesl}
                \end{itemize}
                \item Nazi:
                \begin{itemize}
                    \item Nazi Germany had ``a distorted vision of national grandeur'' \cite[37]{kallisa}
                    \item Expansion into Europe made Americans fearful because of the image portrayed by the ``distorted vision'' \cite[37]{kallisa}
                    \item Increasing German global influence (e.g. Argentina, Austria) \cite[2]{pyensonl}
                    \item Increasing German focus on cultural and territorial spread pre-WWII \cite[17]{pyensonl}
                    \item The Germans were looking to create a Nordic Europe \cite[192]{guettelj}
                    \item The Germans, among other regions, had extensive propaganda distribution in Latin America, which it planned to use as leverage against the United States \cite[59]{krise}
                    \item The German government employed self-victimization to get popular support for expansion into areas populated by Germans \cite[1]{bergend}
                \end{itemize}
            \end{itemize}
        \end{itemize}

    %--------------------------------------------------------------------------------------------------%

    \section{Evaluation of Sources} % O + P + 2V + 2L
    
        The author of the article \textit{Dividing the Indivisible: The Fissured Story of the
        Manhattan Project}, Margot Norris, is a female professor of English and Comparative
        Literature at the University of California, Irvine. Norris' purpose in writing this article
        is to separate the facts of the Manhattan Project from the myths, her thesis being that the
        actual ambitions of the Manhattan Project were hidden from the public as political policy,
        with stated ambitions feeding misinformation to the public as part of propaganda. A value of
        the origin is that the author is a professor of English, and brings a new perspective to the
        topic. A limitation of the origin is that the author's field is not focused on history,
        causing the author to have limited resources for research. The value the purpose is that it
        incorporates the political perception of the Manhattan Project, which is highly relevant in
        understanding the role of fear of German expansion. The limitation of the purpose is that it
        is more focused on the role of the US in the Manhattan Project, with a lack of sources from
        foreign countries, and thus a lack of a foreign perspective.

        The author of the book \textit{Cultural imperialism and exact sciences: German expansion
        overseas, 1900-1930}, Lewis Pyenson, is a professor of the History of Science with a Ph.D.
        from Johns Hopkins University. He is the author of books many about mathematics and physics
        in Germany. The purpose of this book is to evaluate the increasing influence of Germany
        towards the beginning of World War 2, with the thesis being that Germany's scientific
        prowess led to its increasing influence around the world. The value of the origin is that as
        a Professor of History, Pyenson has access to large amounts of resources concerning the
        topics he has written about in his book. The limitation of the origin is that the author may
        not consider political and social issues in his analysis. The value of the purpose is that
        it provides a direct insight into the relation between German expansion and scientific
        development. The limitation of the purpose is that it does not focus on the involvement of
        politics to the extent that it does the sciences.


    % German scientists went to Germany and helped with Germany's atomic weapons program, pressuring America to produce its own competing atomic weapons program out of fear that Germany would develop an atomic weapon first. (Powers 6; Stoff 136).

    \section{Analysis}

        German expansion's correlation on the Manhattan Project can be described through three
        different categories: fear of Germans by the Americans, competition to produce weapons, and
        propaganda. All are evidence of German expansion. Fear of Germans constitutes the American
        perception of the Germans, weapons development competition constitutes the American reaction
        to German expansion, and propaganda on the part of the Germans is direct evidence of their
        desire to expand; American counter-propaganda, on the other hand, falls between the
        categories of perception and reaction.

        The American government feared the production capabilities of Germany, perceiving them as
        the only enemy with the capacity to take advantage of information taken from the Americans
        (Groves 6). This belief alone provides insight on the perspective Americans had of Germans:
        the German state as a technologically advanced country capable of scientific and industrial
        development on a scale comparable to the United States. The big fear was that this
        development capacity would go towards producing an atomic weapon that could be used against
        the United States \cite[136]{stoffm}. Leo Szilard---a physicist and refugee from Germany---brought
        information on German atomic weapons development to Roosevelt, asking him to consider
        development of atomic weapons technologies \cite[12]{norrism}. Roosevelt, soon after that, created
        the Manhattan Project \cite[12]{norrism}. The original objective of the Manhattan Project was, in
        fact, to have security from Germany \cite[140]{grovesl}. With this information in mind, it becomes
        easier to see that fear of Germans was partially a motivating factor for founding the
        Manhattan Project.

        The competition between the Americans and the Germans to produce weapons was also a
        motivating factor for creating the Manhattan Project. When German scientists went to Germany
        to contribute to atomic weapons development, the United States felt pressured to produce a
        competing atomic weapons program to prevent Germany from acquiring an atomic weapon first
        (Powers 6; Steinberg 88). This pressure was increased after German pursuit of rocket
        technology. Rockets constituted a loophole in the Versailles treaty, allowing Germany to
        potentially build up an arsenal of weaponry that could operate at ranges far enough to
        attack America (Neufeld 2; Neufeld 157). Rockets could be used to deliver nuclear warhead
        payloads, which made them particularly appealing to the Germans \cite[157]{neufeldm}. The United
        States, in trying to deter a nuclear first-strike by Germany, created the Manhattan Project
        as a competing nuclear weapons program to Germany's nuclear weapons program \cite[89]{steinbergg}.

        Propaganda campaigns on both sides, American and German, shed some light into both the fear
        and weapon-competition issues; the Germans were, with their expansion, looking to create a
        Nordic Europe, using their control of the press to gain popular support (Guettel 142; Bergen
        1). What made this desire to expand disturbing to the Americans was the perception that the
        Germans had a distorted national vision \cite[37]{kallisa}. The Germans already had influence---
        through extensive propaganda---in the Latin American region, planning to use their cultural
        and political influence in the region as leverage against the Americans (Pyenson 2,17). The
        fact that Germany had a foothold so close to the American homeland brings the issue into the
        realm of fear; given that the Germans were so aggressive with their expansion, the fact that
        they were ``on the doorstep'', so to speak, of the Americans was disturbing, causing no end
        of counter-propaganda by the American government \cite[2]{lauriec}. Ultimately, what all of this
        propaganda meant with regards to the Manhattan Project is simple: deterrent \cite[140]{grovesl}.
        The Manhattan Project could help deter expansion by the Germans, allowing for increased
        safety from German aggression \cite[140]{grovesl}.

    %--------------------------------------------------------------------------------------------------%

    \section{Conclusion}

        Fear of Germans, competition to produce weapons, and propaganda against Germans all tie back
        to the fact that the Germans were more aggressive in their expansion in the decade before
        the creation of the Manhattan Project. A common belief is that the Manhattan Project was
        created to end the war in the Pacific; this is not, in fact, true. While United States
        policymakers only funded the Manhattan Project in 1941, when the public's attention was
        captured by the Pacific war, the perception that the Manhattan Project was created to end
        the second World War was the product of a propaganda campaign after the war to justify the
        usage of nuclear weapons on Japan \cite[12]{norrism}. Ultimately, the Manhattan Project's creation
        was influenced by Germany's desire to expand by a great extent between the years of 1932 and
        1942.

    %--------------------------------------------------------------------------------------------------%

    \printbibliography
\end{document} 